---
output:
  pdf_document:
    includes:
      in_header: well_report.tex
    latex_engine: xelatex
    pandoc_args: ["--variable=geometry:paperwidth=8.5in,paperheight=8in,margin=0.25in"]
params:
  well_id: NULL
  well_location: NULL
  well_tag_number: NULL
  aquifer_num: NULL
  aquifer_type: NULL
  model_type: NULL
  latest_date: NULL
  start_year: NULL
  table: NULL
header-includes:
  - \usepackage{multicol}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(gt)
```

\vspace*{-1.5cm}

\begin{center}
{\large \textbf{Observation Well `r paste0(params$well_id, " - ", gsub("&", "\\\\&", params$well_location))`}}
\vspace{-1.2em}
\end{center}

\begin{center}
\textbf{`r params$aquifer_type` Aquifer | Data since `r params$start_year`| Latest data `r format(params$latest_date, "%b-%d")` | Forecast issued: `r format(Sys.Date(), "%b-%d")`}
\vspace{-1.5em}
\end{center}

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\centering
\includegraphics[width=8in]{Well_`r params$well_id`_plot.pdf}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\centering
\end{minipage}
\end{center}

\begin{center}
{\large \textbf{`r paste0(params$well_id)` - Likelihood (\%) of Groundwater Level Conditions}}
\vspace{-1.5em}
\end{center}

```{r table}
params$table %>% 
  tab_options(latex.use_longtable=TRUE,
              table.font.size = px(12))
```

\begin{wrapfigure}{r}{0.4\textwidth}
  \centering
  \vspace{-10pt}
  \vspace{-10pt}
\end{wrapfigure}

\scriptsize 
\begin{multicols}{2}

\textbf{Note}: Forecasts provide a range of possible conditions and are presented as likelihoods of groundwater being above, below, or near normal. This analysis uses the “normal” term solely in reference to water levels between the 25th to 75th percentiles of historical data, not to imply a steady state baseline for a well. Data should be interpreted with the context of long-term records, patterns, and trends.

\columnbreak

\textbf{Disclaimer}: Groundwater level forecasts use computational models and third-party data. These models have both systematic (model limitations) and random (input data) errors. Forecasts may differ from actual observations and water levels could exceed forecast bounds. Users must accept responsibility for their use and interpretation. Real-time observed data may be subject to change.

\end{multicols}

\begin{center}
{\small Model Information: \textcolor{blue}{\href{https://nrs.objectstore.gov.bc.ca/rfc-conditions/groundwater_forecast/documentation/gw_forecast_overview.pdf}{Overview}} |\textcolor{blue}{\href{https://nrs.objectstore.gov.bc.ca/rfc-conditions/groundwater_forecast/documentation/gw_forecast_chart_details.pdf}{Detailed explanation of chart}} | \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/drought-flooding-dikes-dams/river-forecast-centre}{Technical reference for model}} | \textcolor{blue}{\href{https://governmentofbc.maps.arcgis.com/apps/webappviewer/index.html?id=9f97b3e9e3754ea6b769efe0bbdf3acb}{Forecast Map}} | \textcolor{blue}{\href{https://nrs.objectstore.gov.bc.ca/rfc-conditions/groundwater_forecast/outputs/Groundwater_Drought_Forecast_Report.html}{Forecast Report}}\\

Well Information: \textcolor{blue}{\href{`r paste0("https://aqrt.nrs.gov.bc.ca/Data/Location/Summary/Location/",params$well_id,"/Interval/Latest")`}{Real-time Data}} | \textcolor{blue}{\href{`r paste0("https://bcrfc.env.gov.bc.ca/Real-time_Data/Interactive_Q_process/InteractivePlots/groundwater_levels/",params$well_id,"_dailyWL.html")`}{Interactive hydrograph}} | \textcolor{blue}{\href{`r paste0("https://apps.nrs.gov.bc.ca/gwells/well/", params$well_tag_number)`}{Well summary}} | \textcolor{blue}{\href{`r paste0("https://apps.nrs.gov.bc.ca/gwells/aquifers/",params$aquifer_num)`}{Aquifer summary}} | \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/groundwater-wells-aquifers/groundwater-observation-well-network}{PGOWN}}
}

Issued by \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/drought-flooding-dikes-dams/river-forecast-centre}{BC River Forecast Centre}} on `r format(Sys.time(), "%Y-%m-%d %H:%M")`

\end{center}

